---
title: "RT-qPCR Standard Curve Analysis"
output: html_notebook
---
This code is written to analyse RT q-PCR results from qTower Analytic Jena. 

Getting the dataset: 
Upload the data (Open Project...)from the qTower into qPCRsoft4.1 software.
When setting dilution series in *Settings* make sure the first single numbers are labeled with 01...09 (Name of Standard: Std0 for the single digits, then Std 10 etc.). Set all triplicates in dilutions from 1 to 12 and label with the gene accordingly. 
Then get *Absolute Quantification* and from the table save a csv file for each gene. Make sure the table is sorted by *gene*.

Executing chunk by *Cmd+Shift+Enter* while curser is placed in chunk. 

```{r}
#── Attaching packages ─────────────────────────────────────── 
library(growthcurver)
library(ggplot2)
library(tidyverse)
library(dplyr)
library(ggprism)
```

```{r}
#── get a list of all the CSV files in the directory
csv_files <- list.files(pattern = "*.csv")

```

```{r}
#── Name gene here ─────────────────────────
#graph_title <- 'SOX2'
#csv.file <- '20230303_SOX2.csv'
```

```{r}
#── Upload data set and delete unneeded information ─────────────────────────
# define a function to read in and process each file
process_csv <- function(file) {
  dataset <- read.csv(file,
# Note that the qTower program is giving European csv standards (columns separated by ; and decimals as ,)
    skip = 19,  sep = ';', dec = ',')
dataset[dataset == "" | dataset == " "] <- NA

#Exclude unnecessary columns, make a dataset containing only the datat used
dataset <- subset(dataset, select = -c(Well, X, Mean.Conc., Std.Dev..Mean.Conc.))
results_gene <- dataset %>% filter(!is.na(Gene))

#── Check NTCs ─────────────────────────
NTC <- filter(results_gene, results_gene$`Sample.type` =="NTC") 
}

# apply the function to each file in the list
NTC <- lapply(csv_files, process_csv)

NTC
```


```{r}
plot_csv <- function(file) {
  dataset <- read.csv(file,
                      
 # Note that the qTower program is giving European csv standards (columns separated by ; and decimals as ,)
    skip = 19,  sep = ';', dec = ',')
dataset[dataset == "" | dataset == " "] <- NA

#Exclude unnecessary columns, make a dataset containing only the datat used
dataset <- subset(dataset, select = -c(Well, X, Mean.Conc., Std.Dev..Mean.Conc.))
results_gene <- dataset %>% filter(!is.na(Gene))
                      
#── Filter and plot all data ─────────────────────────

ggplot(results_gene, 
       aes(x=Sample.name, y=Mean.Ct)) + 
  labs(title= file) +
  geom_point() +
   geom_errorbar(aes(ymin=Mean.Ct-Std.Dev..Ct, ymax=Mean.Ct+Std.Dev..Ct), width=.2,
                 position=position_dodge(0.05)) 
}
# apply the function to each file in the list
g <- lapply(csv_files, plot_csv)

g
```



```{r}
fit_csv <- function(file) {
  dataset <- read.csv(file,
                      
 # Note that the qTower program is giving European csv standards (columns separated by ; and decimals as ,)
    skip = 19,  sep = ';', dec = ',')
dataset[dataset == "" | dataset == " "] <- NA

#Exclude unnecessary columns, make a dataset containing only the datat used
dataset <- subset(dataset, select = -c(Well, X, Mean.Conc., Std.Dev..Mean.Conc.))
results_gene <- dataset %>% filter(!is.na(Gene))
                      
#── Based on the graph, select dilutions that fit the standard curve
results <- results_gene %>% filter(Sample.name%in% c("Std01", "Std02","Std03", "Std04","Std05", "Std06", "Std07", "Std08"))

#── Adding a linear regression
ggplot(results,
       aes(x = Conc..Std. , y = Mean.Ct)) +
    geom_point() +
    geom_errorbar(aes(ymin=Mean.Ct-Std.Dev..Ct, ymax=Mean.Ct+Std.Dev..Ct), width=.2,
                 position=position_dodge(0.05)) +
    scale_x_continuous(trans = 'log10') +
    stat_smooth(method = "lm",
             geom = "smooth")

#── Getting linear regression parameters
regression_mean <- lm(Mean.Ct ~ log10(Conc..Std.) , data = results)
summary(regression_mean)

#──  Calculate the efficiency 
intercept <- as.numeric(regression_mean$coefficients[1])
slope <- as.numeric(regression_mean$coefficients[2])

#──  Calculate 2 predicted Ct values
# Ct_mean = slope*(log(Qty)) + intercept
y1=slope*log10(results$Conc..Std.[1]) + intercept
y2=slope*log10(results$Conc..Std.[5]) + intercept
dCt=y2 - y1
dlogCN= log10(results$Conc..Std.[5]) - log10(results$Conc..Std.[1])
ratio = dCt/dlogCN ## this is the slope of the linear regression
efficiency = 10^(-1/slope)
efficiency
efficiency_percentage = efficiency * 100 / 2
efficiency_percentage

label_efficiency <- "Efficiency: "
label_efficiency <- paste0(label_efficiency, as.character(format(efficiency, digit=4)))

label_efficiency_percentage <- "Efficiency: "
label_efficiency_percentage <- paste0(label_efficiency_percentage, as.character(format(efficiency_percentage, digit=4)), "%")

label_r<-"R-squared: "
label_r <- paste0(label_r, as.character(format(summary(regression_mean)$r.squared), digit=3))

label_slope<-"Slope: "
label_slope <- paste0(label_slope, as.character(format(ratio, digit=4)))

ggplot(results, 
       aes(x = Conc..Std. , y = Mean.Ct)) + 
  labs(title= file) +
    geom_point(color = "black",  size = 2) +
    geom_errorbar(aes(ymin=Mean.Ct-Std.Dev..Ct, ymax=Mean.Ct+Std.Dev..Ct), width=.2,
                 position=position_dodge(0.05), color = "gray") +
    theme_prism(base_size = 14)  +
  theme(aspect.ratio = 0.8) +
  scale_shape_prism() + 
   scale_x_continuous(trans = 'log10') +
    stat_smooth(method = "lm",
             geom = "smooth", color = "#FF9999", size=0.75) +
  annotate("text", x = 0.06, y = 28, label = label_r) + 
  annotate("text", x = 0.06, y = 30, label = label_slope) + 
  annotate("text", x = 0.06, y = 26, label = label_efficiency) +
  annotate("text", x = 0.06, y = 24, label = label_efficiency_percentage)
}

f <- lapply(csv_files, fit_csv)

f
```



